Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-17 paper/structureScene.tex
Edit conclusion

This paper presents a new approach for modeling acoustic scenes which utilizes scattering transforms at small scales and a cluster-based representation at large scales. Compared to traditional models based on BOF and summary statistics, this representation allows for the characterization of distinct sound events superimposed on a stationary texture, a concept which has strong grounding in the cognitive psychology literature. In order to extend the selectivity potential of late integration using SVMs to the unsupervised case, we develop the cluster-based model and validate it using experiments on acoustic scene similarity retrieval. For this task, we show significant improvements over the traditional BOF and summary statistics models based on both standard MFCCs and scattering features.
These outcomes shall be studied further in future work by considering larger databases and emerging tasks in computational bioacoustics \cite{wimmer2013sampling}.
\vl{The verb utilize should be avoided.}

>>>>

This paper presents a new approach for modeling acoustic scenes based on scattering transforms at small scales and cluster-based representations at large scales. Compared to traditional BOF and summary statistics models, this representation allows for the characterization of distinct sound events superimposed on a stationary texture, a concept which has strong grounding in the cognitive psychology literature. To adequately capture such distinct events, we develop a cluster-based model and validate it using experiments on acoustic scene similarity retrieval. For this task, we show significant improvements over the traditional BOF and summary statistics models based on both standard MFCCs and scattering features.
These outcomes shall be studied further in future work by considering larger databases and emerging tasks in computational bioacoustics \cite{wimmer2013sampling}.
